Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-23 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
2020 edits, manuscrpt model

**Overall Mean Catch Crabs/Hectare:** `r overall_mean`

**Stations with no catch:** `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`

@@

# Crab/hectare Models {.tabset .tabset-pills}

@@

>>>>

**Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`

**Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%

@@

# East-West Models {.tabset .tabset-pills}

@@

# Manuscript Model {.tabset .tabset-pills }

## Model Dataset

```{r}
start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
overall_mean <- mean(seamap_west$cpue_towspd, na.rm = T)
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()
```

* Total Number of Stations = `r nrow(seamap_west)`

 * Starting in `r start_year` and continuing through `r end_year`

 * Total Sapidus Caught was `r total_catch`

 * Overall Frequency of Occurrence was `r overall_foa`

 * Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`

 * Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%

## Yearly Catch Plot

## Region - Season Plot

## Seasonal Catch Plot

## Candidate Models

#Candidate 1 - no interactions
candidate_1 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
            #year_f * region + 
            offset(log(area_hectares)),
            data = seamap_west)

#Candidate 2 - year * region
candidate_2 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
            year_f * region + 
            offset(log(area_hectares)),
            data = seamap_west)

#Candidate 3 - year * season
candidate_3 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
            year_f * season + 
            offset(log(area_hectares)),
            data = seamap_west)

#Candidate 4 - region * season
candidate_4 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
            region * season + 
            offset(log(area_hectares)),
            data = seamap_west)

#Candidate 5 - year * region + region * season
candidate_5 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
            year_f * region + region * season +
            offset(log(area_hectares)),
            data = seamap_west)

model_list <- list(
  "no interactions" = candidate_1,
  "year * region" = candidate_2,
  "year * season" = candidate_3,
  "region * season" = candidate_4,
  "all interactions" = candidate_5
)

model_aic <- map(model_list,AIC)
model_aic <- bind_rows(
  imap(model_aic, function(x,y) {
    aic_df <- data.frame("Formulation" = y, AIC = x) }
    )
  )
model_aic %>% mutate(`Delta AIC` = AIC - min(AIC)) %>% knitr::kable()

best_mod <- candidate_2
rm(candidate_1, candidate_2, candidate_3, candidate_4, candidate_5)
```

## Catch per Hectare Plot
